\makequotation{It is a pleasure to see a student text that emphasizes the production of real useful software. I also applaud the emphasis on getting results early in the process. Nothing stimulates student morale and activity more.} {Prof. Frederick P. Brooks, Jr., Turing Award winner and author of \emph{The Mythical Man-Month}}

\makequotation{I'd be far more likely to prefer graduates of this program than any other I've seen.} {Brad Green, Engineering Manager, Google Inc.}

\makequotation{Many congratulations\ldots Very proud of including the SPOC in our redeveloped Bachelors' in Software Engineering degree\ldots{} The book is the best I've bought, within minutes of seeing it at ICSE.}{Ali Babar, University of Adelaide}

\makequotation{A number of software engineers at C3 Energy consistently report that this book and its companion online course enabled them to rapidly attain proficiency in SaaS development.  I recommend this unique book and course to anyone who wants to develop or improve their SaaS programming skills.} {Thomas M. Siebel, CEO, C3 Energy, and founder and former CEO, Siebel Systems (the leading Customer Relationship Management software company)}

\makequotation{We have gone from teaching about 60 graduate students per   year in traditional software engineering to 160 per year using   ESaaS. We have similarly seen a large increase in undergraduate   students. The local community of non-profits has come to depend on us   for software development.}{Prof. Hank Walker, Texas A\&M University}

\makequotation{I love this course so much. It's such an amazing  advancement in [Software Engineering] education, and I've been so proud to offer it for the past 2 years. It is a big learning curve to new instructors and students, but I truly believe it's worth it. My students seem to agree.}{Prof. Kristen Walcott-Justice, University of Colorado---Colorado Springs}


\makequotation{A wide and deep coverage of all you need to get started in the SaaS business.}{Vicente Cuellar, Chief Executive Officer, Wave Crafters, Inc.}


\makequotation{The book filled a gap in my knowledge about cloud computing and the lectures were easy to follow. Perhaps the most exciting part was to write a cloud application, upload, and deploy it to Heroku.}{Peter Englmaier, University of Z\"{u}rich, Switzerland}

\makequotation{An excellent kickstart into Ruby, Rails and test driven approaches. The fundamentals have been covered with great depth and experience, it's the perfect introduction to modern web development. It should be a requisite for new engineers.}{Stuart Corbishley, Clue Technologies/CloudSeed, South Africa.}

\makequotation{An excellent book that will have you up and running   building SaaS apps progressively in a few short days. The screencasts   and the GitHub Gists are invaluable. A very practical approach to   Agile software development.
%% You won't know it but you would have
%% picked up software engineering techniques without even knowing you are
%% doing it!
}{Prof. Rakhi Saxena, Assistant Professor, Delhi University, India}

\makequotation{The authors have accomplished a very welcome   juxtaposition of theory and practice for any modern beginning to   advanced Software Engineering course \ldots
%% On the one hand, they cover key
%% Software Engineering fundamentals including development processes,
%% requirements engineering, testing, software architecture,
%% configuration management, implementation, and deployment. On the other
%% hand, they convey all of this grounded in a ``real-world'' approach
%% centered around Ruby/Rails and its rich ecosystem of agile, test- and
%% behavior-driven development tools and techniques, with a direct avenue
%% to cloud deployment of running, quality software.
I have used the Beta   Edition of this book very successfully in my advanced undergraduate   software engineering course, where it beautifully complements both my   lectures and the team project.}{Prof. Ingolf Krueger, Professor, University of California at San Diego}

\makequotation{A really good introduction book to practical Agile development. All you need is gathered in one book with lots of practical examples.}{Dmitrij Savicev, Sungard Front Arena, Sweden}
