\begin{tabularx}{\fullwidth}{|X|X|X|X|}
\hline
\B{Item} & \B{3 points} & \B{2 points} & \B{1 point}   \\
\hline

\B{Preparation} &
Presentation was rehearsed thoroughly, few hiccups &
Presentation is mostly fluid, with the exception of maybe 1 or 2
underprepared people &
Sloppy presentation, no clear direction or disorganized
\\ \hline

\B{Customer Need} &
&
Included brief statement of customer problem and scope of project &
Not clear what the customer really wanted or what problem the group is
trying to solve
\\ \hline


\B{Technical Discussion} &
Clearly conveyed some technical details of the app.  Discussed a
technical challenge in an understandable way &
Attempted to talk about technical aspects of app, mostly successfully.
Either no technical challenge or not able to clearly convey technical
topics &
Little or no technical coverage of their app.  Implementation details
are unclear.
\\ \hline

\B{Customer Interaction} &
Clearly describe relationship with customer. Talk about goods, bads, and
what was learned &
Talked about customer interaction to some extent &
Mentioned customer interaction, but no details about the experience
\\ \hline

\B{Development Practices} &
Explained clearly their implementation of agile in their iterations.
Reflect on what went well and what did not.  Had a method to taking on
iterations. &
Briefly explain development practices.  Give an idea of approaches they
took to iterations/Agile, but don't reflect on their effectiveness &
Doesn't appear they took methodology seriously, and/or no evidence of
concrete implementation of agile principles
\\ \hline

\end{tabularx}

\begin{tabularx}{\fullwidth}{|X|X|X|X|X}

  \B{Approach} & \B{Technologies \& Tools} & \B{Main Pros} & \B{Main Cons}
  \\  \hline

  Responsive or mobile-only Web site
  &
  HTML5, CSS, JavaScript; any development environment
  &
  Portable across devices, so no need to develop/maintain multiple
  versions; updates automatically
  &
  May not show up in searches; not listed in app stores; may lack
  access to certain platform hardware features, such as
  biometrics-based identification
  \\   \hline

  Native app
  &
  Java (Android) or Objective-C (iOS) with mobile-specific IDE
  &
  Best performance; guaranteed access to all platform hardware features
  &
  Must rely on users to download and install updates; supporting
  multiple platforms requires maintaining multiple codebases

  \\  \hline

  Wrapped app
  &
  HTML5, CSS, JavaScript; framework such as PhoneGap required to
  ``package'' app for distribution
  &
  Portable, develop with any IDE, but still get installable app that
  appears in app stores and searches
  &
  Must rely on users to download and install updates
  \\ \hline

\end{tabularx}
